We did an amazing thing

### 2022-12-28 paper.tex
More images

\subsection{Gaussian mixture}
\label{sec:gauss}
Take $N$ random values $a_i$, $b_i$ and $\sigma_i$. Let $f$ be
\begin{equation*}
  f(x,y) = \sum_{i=1}^N \frac{1}{\sigma_i} \exp(\frac{-(x-a_i)^2-(y-b_i)^2}{\sigma_i^2})
\end{equation*}
Inequality $f(x,y) \le T$ defines a ``blob'' like one which can be seen on
\textcolor{red}{insert picture}. We can use the algorithm developed in
\cref{sec:cool-algo} to compute precise values of $F_{ss}$ for this blob and
compare them with values obtained by using the fast algorithm in section
\cref{sec:algo}. The result of this comparison is on \textcolor{red}{Insert
  picture}. The maximal relative error for values obtained with the fast
algorithm is \textcolor{red}{insert value}.

\section{Improvement of the fast algorithm}
\label{sec:improvement}
Take two 2D images like the ones on \textcolor{red}{insert image}. The
boundaries between black and white cross each other at the angle $\phi$. We
apply the filter $H$ (\cref{eq:filter-3x3-2d}) to each image, multiply results
element-wise and sum all elements of the product. An obtained value must
approximate $1/\sin \phi$ if we want $H$ to be suitable for calculation of
surface-surface function. With filter described in \cref{sec:algo} we get the
following picture \textcolor{red}{insert picture}. We see that $H$ approximates
$1/\sin \phi$ not very good.

Now, let's try a wider filter $H'$:
\begin{align}
  H'_{ij} &= \frac{1}{30} \left[
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & -24 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array}
    \right] \label{eq:filter-5x5-2d} \\
  H'_{ijk} &= \frac{1}{150} \left[
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array} ;
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & -124 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array} ;
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array}
    \right] \label{eq:filter-5x5-3d}
\end{align}
With this filter we get a different picture \textcolor{red}{insert image}. A
comparison of the fast algorithm with a wider filter kernel with a precise
calculation for a ``blob'' show in \cref{sec:gauss} is show on
\textcolor{red}{insert image}. The maximal relative error is reduced to
\textcolor{red}{insert image}.

>>>>

\subsection{Gaussian mixture}
\label{sec:gauss}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth, frame]{images/blob.png}
  \caption[]{An example of a ``blob'' generated by Gaussian mixture $f(x,y)$
    which consists of four Gaussian functions. White area is where
    $f(x,y) \le 3$.}
  \label{fig:blob}
\end{figure}
Take $N$ random values $a_i$, $b_i$ and $\sigma_i$. Let $f$ be
\begin{equation*}
  f(x,y) = \sum_{i=1}^N \frac{1}{\sigma_i} \exp(\frac{-(x-a_i)^2-(y-b_i)^2}{\sigma_i^2})
\end{equation*}
Inequality $f(x,y) \le T$ defines a ``blob'' like one which can be seen on
\cref{fig:blob}. We can use the algorithm developed in \cref{sec:cool-algo} to
compute precise values of $F_{ss}$ for this blob and compare them with values
obtained by using the fast algorithm in section \cref{sec:algo}. The result of
this comparison is on \cref{fig:fss-blob}. The maximal relative error for values
obtained with the fast algorithm is \textcolor{red}{insert value}.
\begin{figure*}[!pt]
  \centering
  \subfigure[$3\times 3$ kernel $H$]{
    \includegraphics[width=0.45\linewidth]{images/fss-blob-3x3.png}
    \label{fig:fss-blob-3x3}}
  \hfill
  \subfigure[$5\times 5$ kernel $H'$]{
    \includegraphics[width=0.45\linewidth]{images/fss-blob-5x5.png}
    \label{fig:fss-blob-5x5}}
  \caption[]{Plot of the surface-surface function for the blob on
    \cref{fig:blob}. Values of $F_{ss}$ were calculated in semi-circle with
    radius $R = 0.3$ and angle $\phi$ varying from $0$ to $\pi$. Resolution of
    the image varies from $500\times 500$ pixels to $3000\times 3000$.}
  \label{fig:fss-blob}
\end{figure*}

\section{Improvement of the fast algorithm}
\label{sec:improvement}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/experiment-setup.png}
  \caption[]{Left, center: images $A$ and $B$ used in the experiment described
    in \cref{sec:improvement}. Right: Interfaces between phases are line
    segments which intersect each other at angle $\phi$. Shaded area is where
    $(H*A)\cdot(H*B)$ has non-zero values.}
  \label{fig:experiment-setup}
\end{figure}
Take two 2D images like the ones on \cref{fig:experiment-setup}. Boundaries
between black and white cross each other at the angle $\phi$. We apply the
filter $H$ (\cref{eq:filter-3x3-2d}) to each image, multiply results
element-wise and sum all elements of the product. An obtained value must
approximate $1/\sin \phi$ if we want $H$ to be suitable for calculation of
surface-surface function. With filter described in \cref{sec:algo} we get a
picture as on \cref{fig:angles-3x3}. We see that $H$ approximates
$1/\sin \phi$ not very good.

Now, let's try a wider filter $H'$:
\begin{align}
  H'_{ij} &= \frac{1}{30} \left[
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & -24 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array}
    \right] \label{eq:filter-5x5-2d} \\
  H'_{ijk} &= \frac{1}{150} \left[
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array} ;
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & -124 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array} ;
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array}
    \right] \label{eq:filter-5x5-3d}
\end{align}
With this filter we get a different picture (\cref{fig:angles-5x5}). A
comparison of the fast algorithm with a wider filter kernel with a precise
calculation for a ``blob'' show in \cref{sec:gauss} is show on
\cref{fig:fss-blob-5x5}. The maximal relative error is reduced to
\textcolor{red}{insert image}.
\begin{figure*}[!pt]
  \centering
  \subfigure[$3\times 3$ kernel $H$]{
    \includegraphics[width=0.45\linewidth]{images/angles-3x3.png}
    \label{fig:angles-3x3}}
  \hfill
  \subfigure[$5\times 5$ kernel $H'$]{
    \includegraphics[width=0.45\linewidth]{images/angles-5x5.png}
    \label{fig:angles-5x5}}
  \caption[]{dfdfdfdf}
  \label{fig:angles}
\end{figure*}
